PyPy's Approach to Virtual Machine Construction

### 2006-07-12 talk/dls2006/paper.tex
Carl's suggestion
sabi's suggestion

PyPy achieves this goal without giving up on the efficiency of the
compiled VMs, or keeping it within reach of further reasonable
optimization work.

>>>>

PyPy achieves this goal without giving up on the efficiency of the
compiled VMs, thereby keeping it within reach of further reasonable
optimization work.
